---
bibliography: bibliography/references.bib
csl: bibliography/nature.csl
output:
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::word_document2: 
      toc: false
      toc_depth: 3
      reference_docx: templates/word-styles-reference-01.docx
      number_sections: false 
  bookdown::html_document2: default
documentclass: book
---

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:tri-quote)', echo = TRUE}
Next on my list of features to be specially considered I would place the consistency
of the observed association. Has it been repeatedly observed by different persons, in different places, circumstances and times?
```
(ref:tri-quote) --- Sir Austin Bradford Hill, 1965 [@hill1965]

<!-- TODO Add this to the Chapter summary in the introduction -->

<!-- ### Triangulation  -->

<!-- TODO Have a look at this - potentially move to triangulation chapter -->

<!-- One key question for which multiple distinct sources of evidence were available were those looking at Laz -->

<!-- Consideration of the potential impact of the magnitude and direct of residual confounders/bias is not a major stretch from what is already happening in the assessment of the quality of evidence (GRADE) framework. Within GRADE, the overall quality of evidence can be upgraded when there is deemed to be unmeasured or residual confounding variables which reduce the. For example, if the propensity to treatment is related to comorbidity burden, but those on treatment still have better outcomes then those on control, it is likely that the true effect of the intervention is being underestimated. [@guyatt2011] -->

# Aetiological triangulation across evidence sources {#tri-heading}

\minitoc <!-- this will include a mini table of contents-->

```{r, echo = FALSE, warning=FALSE, message=FALSE}
source("R/helper.R")
knitr::read_chunk("R/05-Code-CPRD-Analysis.R")
knitr::read_chunk("R/07-Code-Triangulation-Analysis.R")
doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
```

## Lay Summary

Triangulation is the practice of using multiple sources of evidence to provide more reliable answers to a research question. Different sources of evidence will have different limitations. If the result from each source points towards the same answer, this improves our confidence in the conclusion.

<!----------------------------------------------------------------------------->
&nbsp;

## Introduction

This chapter will attempt to triangulate the evidence identified by the systematic review in Chapter \@ref(sys-rev-heading-results), with the the results from the analysis of CPRD data (Chapter \@ref(cprd-heading) and IPD \@ref(ipd-heading).

&nbsp;<!----------------------------------------------------------------------->  

### Overview of triangulation {#triangulation-overview}

Aetiological triangulation, or simply triangulation, is the process of comparing and contrasting across result in order to . 



It has been widely used in the literature, and is comparable to Bradford-Hill's criteria of "consistency", that is the replication of an observed relationship across several different contexts.[@hill1965] In this framework, 

&nbsp;<!----------------------------------------------------------------------->  

### Terminology

__Different types of triangulation__

_Qualitative_ triangulation is describing the different results. It regularly appears though not under that name, in the discussion of results section under the name "comparison with other literature". 

Previous examples of this approach have used criteria such as  

In contrast, _quantitative triangulation_ attempts to obtain a overall numerical result by synthesising the different types of evidence.

However, previous attempts at triangulation ignore the potential for varying and opposing sources of bias within a evidence source. For example, 

The terminology used in describing different mechanisms by which an observed result may  complicate interpretation. This section clearly defines how each are used in h

Here, internal bias is used in terms of 

In contrast, external bias (also called indirectness, or )

Additionally, potential biases can be additive or proportional. Pro

Talk about problems of sclae - assuming bias direction at the study level works well if you only have one study per design category as in the example by Ference et al (e.g. IPD analysis of ) 

&nbsp;<!----------------------------------------------------------------------->  

## Methods
### Data sources

As outlined in the thesis overview presented in Section \@ref(background-thesis-overview), the triangulation draws on the research produced in the preceding chapters.

This chapter builds on the comprehensive systematic review presented in CHapter \@re(sys-rev-heading), and incorporates the results of the analyses presented in Chapters \@ref(cprd-heading) (statins on dementia outcomes in the CPRD) & \@ref(ipd-heading) (lipids on dementia outcomes in IPD).

Table \@ref(triSummary) illustrates the causal question each approach attempted to answer, along with the exposures and outcomes for each.

<!----------------------------------------------------------------------------->
(ref:triSummary-caption) triSummary

(ref:triSummary-scaption) triSummary

```{r triSummary-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->

&nbsp;<!----------------------------------------------------------------------->  

### Qualitative triangulation

As a first step to assessing the evidence, all evidence sources were grouped by outcome and compared and contrasted. Potential reasons for heterogeneity were examined with specific reference to the risk of bias assessments performed. 

This analysis built on the detailed risk of bias assessments performed and presented as part of the systematic review (Chapter \@ref()/\@ref()), and the results of the



&nbsp;<!----------------------------------------------------------------------->  

### Quantitative triangulation

In addition to the qualitative discussion of evidence, I attempted to integrate the numerical results of the multiple approaches.

A framework for bias-adjusted meta-analysis

The code supporting the original implementation (written as a STATA do file) was converted into R code, and 

This approach incorporated advancements in the way that bias in results is assessed to illustrate both how causal questions could be addressed under this quantitative triangulation framework, and 

This was implemented via a bias-adjusted meta-analytical framework.

Several steps were used to accomplish this approach, as described in the following sections. As an illustrative example, the approach was implemented first for a single result and then for all results related to two causal questions of interest, as defined in the following section.

&nbsp;<!----------------------------------------------------------------------->  

#### Definition of the causal questions of interest (case-studies)
<!-- TODO See ROBINS-E for this, as to how to think about exposures, adn the "Duration and timing of exposure being assessed with different approachesDuration and timing of exposure being assessed with different approaches" section of the aetiological triangulation -->

In the first instance, following standard triangulation

This chapter will consider two questions

Firstly, an ter

Secondly an 

Background to the causal question

Following best practice guidance, three 

Table with columns describing exposure, outcome, time-point, other aspects (cumulative), and

This was also guided by the forthcoming ROBINS-E tool, which has

*	Effect of average exposure to LDL-c during midlife on AD 
*	Effect of cumulative LDL-c from birth to mid-life on AD
* Effect of late-life LDL-c on all-cause dementia

&nbsp;

<!-- TODO This table will describe the causal questions of interest, following the ROBINS-E framework as columns, and list the included studies adn the relative weights of each. -->

<!----------------------------------------------------------------------------->
(ref:questionsOfInterest-caption) questionsOfInterest

(ref:questionsOfInterest-scaption) questionsOfInterest

```{r questionsOfInterest-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->

&nbsp;

a)	Proposed method for this chapter
i)	Example: LDL-c at midlife on Alzheimer’s disease risk
ii)	Specific causal effect of interest using ROBINS-E framework:
•	Population of interest: General population
•	Exposure of interest: Low density lipoprotein cholesterol
•	Exposure window of interest: Midlife (45-60)
•	How exposure over time should be summarized: Cumulative exposure
iii)	Identify relevant studies from evidence base
•	LDL-c assessed at midlife
•	MR of LDL-c
•	Statin use at midlife
iv)	Assess risk of bias in each result, define expected directions of each bias and plot
 
v)	Assign additive value to each level of bias (High = 0.2, Some concerns =0.1, Low = 0), assign sign to these values based on predicted direction and sum across result
vi)	E.g. for effect estimate 0.71 (0.57-0.89):

Element	D1	D2	D3	D4	D5	D6	D7	Overall
Bias	High	Some concerns	Low	Low	Low	Some concerns	Some concerns	Serious
Direction	Left	Away from null	-	-	-	Towards null	Away from null	
Modifier	-0.2	-0.1	0	0	0	0.1	-0.1	-0.3

vii)	Assign a proportional value representing the indirectness for each result
•	Statin studies would give smaller proportion (e.g. 0.7) of effect observed for generally lower lipids, as they would reduce cumulative exposure 
•	SNPs predict quite strongly LDL-c and so would have minimal indirectness
viii)	Combine in a bias-adjusted meta-analysis 


&nbsp;<!----------------------------------------------------------------------->  

####	Identify relevant studies

Once the causal question of interest had been defined, studies related to it were 

&nbsp;<!----------------------------------------------------------------------->  

####	Assess risk of bias in each result, define expected directions of each bias

Within our framework and as part of the risk-of-bias assessments reported in \@ref(risk-of-bias-subheading), I attempted to records the direction of the bias, so that it could feed into the triangulation. 

All of the risk-of-bias tools 

In addition, the tool also aim to capture the potential direction of bias for each result. Possible responses included: "Favours experimental", "Favours comparator", "Towards null", "Away from null", and "Unpredictable". Highlight that this is slightly different for the confounding domain in non-randomised studies, which only allows for the "Favours experimental", "Favours comparator", and "Unpredictable" options..

These levels only apply to existing tools, not the MR tool. However, a similar approach was employed.

Of note, the guidance for the tools suggests that if assessors are not able to articulate why the bias in a given domain will "pull" the observed estimate in a specific direction, they should not try to guess. 

To assess the usefulness of this system, the number of domains for which bias was expected (i.e. judged to be a more than Low risk of bias) but for which no expected direction could be identified were expressed as a percentage. If this percentage is high, the helpfulness of the approach is 

In line with best practice for meta-analyses, observational studies deemed to be at critical risk of bias were excluded from all quantiative syntheses.

&nbsp;<!----------------------------------------------------------------------->  

#### Mapping between different risk of bias tools

For the sake of consistency, I mapped the different acceptable judgements in each risk-of-bias tool to a harmonised set: "Low", "Moderate","High". The mapping can be seen in Table \@ref(tab:robLevelsMapping-caption).

Of note, no mapping was performed for the critical risk-of-bias levels present in the tools for non-randomised studies of interventions. This is because current best practice in evidence synthesis is to exclude all studies at critical risk of bias for further quantitative synthesis.

&nbsp;<!----------------------------------------------------------------------->  
(ref:robLevelsMapping-caption) robLevelsMapping

(ref:robLevelsMapping-scaption) robLevelsMapping

```{r robLevelsMapping-table, message=FALSE, results="asis", echo = FALSE}
```
&nbsp;<!----------------------------------------------------------------------->  

#### Visually inspect results and bias

In order to aid with the triangulation exercise, I created a new method of presentation of these results was developed to enable detailed comparison across different studies contributing to the causal question.

Similar to the standard paired forest plots introduced in Chapter \@ref(), the level of bias across the domains in each study is reported using coloured blocks. However, in contrast to the previous plots, arrows are used in place to illustrate the predicted direction of bias in that domain, categorised as pulling towards the left or the right.

This second aspect required some additional consideration, given the distinct and competing options available to assessors. For example, the direction of the arrow when the direction of bias is thought to favour the intervention/exposure will be be same regardless of the position of the point estimate. The same is not true for the "Towards the null"/"Away from the null" options. For example, if the effect estimate represents a protective effect (below the null), then bias towards the null would be represented by a right pointing arrow (Figure \@ref(fig:)). In contrast, if the effect of the intervention is harmful (effect estimate above the null), bias towards the null will be represented by a right-pointing arrow. The program to create these figures thus requires knowledge of both the predicted direction of bias and the effect estimate.

Tha

Helper functions in the forthcoming `triangulate` package - see Appendix BLAH.

<!-- TODO include illustrative example here -->

Where the direction of bias was unclear/could not be determined from the report, this is indicated by a dash. 

These graphs were built using the risk of bias tool described in Appendix \ref()

<!-- TODO Does immortal time bias not also have a consistent effect -->


&nbsp;<!----------------------------------------------------------------------->  

#### Types of bias

Additive biases are those independent of the effect estimate - they shift it left or right. These biases are indicated by the "Favours comparator"/"Favours experiment/exposure" options in the 

&nbsp;<!----------------------------------------------------------------------->  

####	Assign modifying values to risk/direction of bias

<!-- TODO Note that they are on the log scale - Lines 45-50 of addbias -->

For example, for a "High" additive bias in $j$th domain of the $i$th study:

$\delta_{ij}^{\mathrm{High}}$

Uncertainty around this estimate, $\delta_{ij}^{\mathrm{High}}$, is given by a distribution:

$$
\delta_{ij}^{\mathrm{High}} = f(\mu_{i,j}^{\mathrm{High}}, \sigma_{i,j}^{\mathrm{High}})
$$

The sign of $\mu_{i,j}^{\mathrm{High}}$ is defined by the relative direction of the bias in relation to the point estimate. If the bias is expected to pull the effect to the left, the position is given a negative sign, and if it is expected to pull the effect to the right, it is given a positive sign.

One key feature of the domain-based risk-of-bias domains is that the domains are considered interchangeable - i.e. a "high" bias in one domain is equivalent to a "high" bias in any other. As such, for this analysis, I assumed that the distributions assigned to each level of bias is contrast across all values of j, or alternatively, is constant across all domains in the risk of bias assessment tool.

$$
\delta_{i,1}^{\mathrm{High}} = \delta_{i,2}^{\mathrm{High}} = ... = \delta_{i,j}^{\mathrm{High}}
$$

and similarly

$$
\delta_{i,1}^{\mathrm{Moderate}} = \delta_{i,2}^{\mathrm{Moderate}} = ... = \delta_{i,j}^{\mathrm{Moderate}}
$$

For the purposes of this example analysis, 

High
Some concerns

These figures were sense-checked against

However, this also allows us to a priori define common modifying values across all domains of bias. In a bias-adjusted meta-analysis using this approach, a high risk of bias in the will have the same modifying effect on the results.

As such, a simulation approach was taken to explore the impacts of several different strategies 


<!-- TODO Discuss proportional versus additive, and the fact that all biases considered previously for internal were deemed to be additive. -->

&nbsp;<!----------------------------------------------------------------------->  

####	Assign modifying values to indirectness

As I am attempting to identify the causal effect across different study designs, I needed to . This is not necessary if just summarising the literature.

A similar approach was used to define prior distributions for external bias or indirectness. I used a similar enforced scale of "Low/"Moderate"/"High" indirectness versus each of the 4 aspects of the target causal question. (recap).

In the original method, this was assessed against 4 categories of internal bias.

In this 

"One important difference between these approaches that will need to be addressed in the triangulation is that RCTs relate to short-term modification of lipid levels, whereas Mendelian randomisation studies typically refer to lifelong exposures; and traditional observational epidemiology approaches may refer to short or longterm exposure (although are often not explicit about this). The triangulation will take these into account, for example by superimposing the studies on a hypothetical model for exposure-outcome relationship across the life course." 

<!-- From NIHR applications -->

<!-- "If the aim of a meta-analysis is to summarize the literature rather than to address a target question, there is no need to adjust for external biases since differences between the (idealized) studies are accepted as diversity. The need to adjust for internal biases remains and our method can be applied directly to these." Taken from https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2667303/ - good explanation on difference between qualitative and quantitative triangulation. -->

####	Combine in a bias-adjusted meta-analysis 

Once the total internal and external additive and proportional biases for each result were computed, they were used to define an adjusted estimate and 

Using the method defined in Turner _et al_,[@turner2009] the adjusted estimate is defined as:

$$
\hat{\theta} = \frac{y_i - \mu_{i\delta}^{\mathrm{I}} - \mu_{i\beta}^{\mathrm{E}}\mu_{i\delta}^{\mathrm{E}}}{\mu_{i\beta}^{\mathrm{I}}\mu_{i\delta}^{\mathrm{E}}}
$$


The standard error of this estimate is then calculated as:

$$
\mathrm{SE}(\hat{\theta})=\left(\frac{1}{\mu_{i \beta}^{\mathrm{I}} \mu_{i \beta}^{\mathrm{E}}}\right)^{2}\left\{s_{i}^{2}+\left(\mu_{i \beta}^{\mathrm{I}} 2+\sigma_{i \beta}^{\mathrm{I}}\right)\left(\hat{\theta}^{2} \sigma_{i \beta}^{\mathrm{E} 2}+\sigma_{i \delta}^{\mathrm{E} 2}\right)+\sigma_{i \beta}^{\mathrm{I}}\left(\hat{\theta} \mu_{i \beta}^{\mathrm{E}}+\mu_{i \delta}^{\mathrm{E}}\right)^{2}+\sigma_{i \delta}^{\mathrm{I} 2}\right\}
$$

Once each individual result has been adjusted, they are combined n a standard random-effects meta-analysis, conducted using the `metafor` R package.

The code to implement this model was obtained via contact with the primary author of the original paper proposing the elicitation. For compatibility, the STATA code was converted to R, and to verify the accuracy of the translation, the results of the original analyses were reproduced (see Appendix \@ref() for details). 


<!-- TODO Deal with the fact that the Panel wasn't super useful -->

&nbsp;<!----------------------------------------------------------------------->  


## Results

### Qualitative triangulation

```{r azd-text, echo = FALSE}
```

#### All-cause dementia

<!-- TODO Need to talk about fibrates here too -->

__Statins and all-cause dementia__

This conflicts with the findings of our analysis, where statin use was associated with an increased risk of all-cause dementia (`r anydem_text`). Some of the included studies in the meta-analysis specifically exclude vascular dementia from the definition of all-cause dementia,[@chao2015] which may limit the ability for comparison with our findings for the all-cause dementia outcome.

Additionally, a previous analysis of the THIN EHR database using a propensity-score matched analysis found a protective effect of statins on all-cause dementia (HR:0.81, 95%CI:0.69-0.96)[@smeeth2009]. 

&nbsp;<!----------------------------------------------------------------------->  

#### Alzheimer's disease

__Statins and Alzheimer's disease__

Our results are broadly in line with the findings of two distinct approaches examining the effect of statin treatment on subsequent Alzheimer's disease. No randomized trials of statins for the prevention of Alzheimer's disease have been reported, but a recent meta-analysis of 20 observational studies found statins were associated with a reduced risk of Alzheimer's disease (RR 0.69, 95% CI 0.60–0.80) with stronger evidence than observed in our analysis.[@poly2020] This review included case-control studies and analyses likely to be at risk of immortal time bias, which may account for the discrepancy with our findings. Additionally, a recent Mendelian randomization study examining the effect of genetic inhibition of HMGCR on Alzheimer’s disease (a genetic proxy for statin treatment) provided equivocal evidence (OR: 0.91, 95%CI: 0.63-1.31) but was consistent with our results.[@williams2020]

Our additional analyses stratified by statin properties found little evidence of differences in associations of lipophilic and hydrophilic statins and incidence of Alzheimer’s disease, consistent with a recent meta-analysis of observational studies.[@chu2018]

&nbsp;<!----------------------------------------------------------------------->  

#### Vascular dementia

__Statins and vascular/other dementia__

Far fewer studies have tested the association between lipid-regulating agents and vascular dementia or other dementias. A recent review found four observational studies examining the association of statins and vascular dementia found limited evidence for an effect (RR:0.93, 95% CI 0.74–1.16).[@poly2020] This contrasts with the harmful association found in our analysis (`r vasdem_text`). When stratifying by lipid properties, lipophilic statins were more harmful than hydrophilic statins in vascular dementia, potentially due to their ability to cross the blood brain barrier.

&nbsp;<!----------------------------------------------------------------------->  

__Other drug classes__

Apart from statins, few studies examining a lipid-regulating agent have been reported (Chapter \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading)). 

One of the few classes for which a evidence was available were fibrates, which found little evidence of an association with all-cause dementia was identified,[@ancelin2012] inconsistent with our finding that patients prescribed fibrates had higher all-cause dementia risk than those prescribed other lipid lowering agents.

A previous Mendelian randomization study found little evidence that genetic variants that proxy for ezetimibe affect risk of Alzheimer’s disease (OR: 1.17, 95%CI: 0.73-1.87),[@williams2020] consistent with our findings. Note that this study was published in 2020 and so was not included in the review.

&nbsp;<!----------------------------------------------------------------------->  

### Quantitative triangulation

#### Single study

Explain how example study was chosen

#### Causal question #1

Including sensitivity analyses

and citations of studies - going to be a bit of pain

#### Causal question #2



&nbsp;<!----------------------------------------------------------------------->  

## Discussion

Summary of risk-of-bias/triangulation results

Percentage of domains for which a direction of bias could be assigned?

Compare bias-adjusted and

See what happens if using additive (l=1,m=2,s=3,c=4) vs multiplicative/log scale (l=1,m=2,s=4,c=8). Present adjusted results and meta-analysis of adjusted results.

Applicability/indirectness as an issue 
Compare with GRADE and cite George's example of 40% of effect predicted by MR seen when using statins for 5 years

### Summary of findings

This chapter has demonstrated how new developments in systematic risk of bias assessment. 

Future quantitative triangulation should move beyond the concept of comparing results at the approach level, and instead focus on the inherent threats to internal validity present in each specific result relevant to the causal question. 

While this makes the process both more labour intensive and complex, to assume that, for example, all retrospective studies are equally at risk is to overlook. While ti could be true that all retrospective studies share some _minimal level_ of bias, there are several opportunities. Failing to separate these the individual results loses information, particularly given the now widespread availability of tools to systematically assess the biases present in each result.

In this chapter, I have presented a new method of visualising both the level and expected direction of bias inherent to each result, and suggested how this could be incorporated with a bias-adjusted meta-analysis approach to work towards a generalised qunatitative triangulation framework. 

I've highlighted the limitations of this method, as the correct distributions of modifying values in each risk-of-bias domain should be driven by meta-epidemiological studies which do not yet exist, framing them as opportunities for future research.

&nbsp;<!----------------------------------------------------------------------->  

###	Limitations and strengths

<!-- TODO See discussion of original Turner paper -->

#### Problems with quantitative triangulation approach

Missing natural variation obtained from elicitation approach. Trade-off between systematic approach presented here and personal variation obtained from several reviewers. 

A potential combination between the two would be to use the variation in risk-of-bias assessments

Elicitation and bias-adjusted not as favoured versus weighting [@stone2020] <!-- TODO Check this is actually what this reference says --> though weighting at the overall risk-of-bias level loses some of the information contained in domain-level based assessments. 

No good information on what the potential distributions for different levels of bias (High vs Moderate vs Low) should be. 

Meta-epidemiological studies on the effect of different methodological issues on results exist for randomised controlled trials,[@amer2021; @page2016] suggesting that X, Y and Z.

However, there is substantially less , arguably because of the absence of clear
Many meta-epi studies of non-randomised studies assume bias at the study-design level, similar to the early triangulation frame-work, rather than considering the actual biases deemed to be present in a given result. In this scenario, study

Potential future meta-epidemiology studies should begin to create these datasets. 

A key example of a useful future study in this domain would be the mining of maximally adjusted vs. unadjusted estimates from abstracts from primary studies to assess the impact of insufficient confounding by topic. However, these datasets could also be built from systematic reviews of a topic, as they would already be gruped by reserach domain and provided the risk of bias data is shared, provide a ready source of information

For example, if it was . New software for performing risk of bias assessments, being developed by the Bristol Appraisal and review of Research group has this as a secondary methodological aim.


&nbsp;<!----------------------------------------------------------------------->  

This approach has a number of advantages. One of the key ones is modifying distributions of each level of bias could be defined _a priori_ in contrast to the .

In addition, the generalised framework will allow for 


#### Subjectivity of risk of bias assessments

By definition, . In this case of this proof-of-concept analysis, the direction of bias was assessed by a single assessor. If attempting to impact policy, the 


#### Defining appropriate levels of bias

In previous attempts at bias/indirectness-adjusted meta-analysis, the extent to each was assessed via a elicitation process using a number of experts.

Ideally, the modifying values

<!-- TODO Pretty sure Julian sent me some papers on have suggested values for randomised controlled trials (e.g. effect of poor blinding etc) -->

i)	Ideally modifying values (both internal and external) would be based on empirical research, but in absence of this, sufficient to model multiple values (High = 0.1, Some concerns =0.05, Low = 0) and relationships (High = 0.3, Some concerns =0.1, Low = 0)? 

Need range around modifying values, as total variance of the biases is added to the total variance of the studies (elicitation on scale presented above asks for range rather than single estimate


Similar there are several examples of usmeta to define priors for other statistical terms in meta-analysis. For example, previous work has looked at het

Like other studies examining the prior distributions of heterogeneity across different topic areas <!-- TODO Cite turner etc -->

Talk about different ways to define bias terms, using expert-elicitation vs .[@rhodes2020]

Also, talk about the fact that much of the bias-adjusted analysis work to date has been done on trials. Describe reasons for this but highlight that for triangulation, there needs to be better coverage of 

&nbsp;<!----------------------------------------------------------------------->  

#### Exclusion of studies at critical risk of bias

One potential - however, the estimation of an appropriate adjustment value for these studies would be substantially more challenging.

In any case, it represented a small number of studies.s

&nbsp;<!----------------------------------------------------------------------->  

#### Type of bias (proportional vs additive) not shown on figure

In contrast

The graphics shown in Section \@ref() do not show the type of bias (additive or proportional), only the direction. While this is acceptable, future work could assess, potentially by using different arrow types to denote the different types of bias.

A key strength of this project is the development of a standardised way of capturing bias domains and converting the.

Helper functions in the triangulate package convert risk-of-bias assessment 

&nbsp;<!----------------------------------------------------------------------->  

#### Challenges of real-life data

Compare and contrast with the nice example presented in the triangulation paper - realities of non-exemplars is that it is very hard to get this right. Also highlight the issue with assigning a direct of bias in many studies

I hope this presents step forward in how researchers think about and visualise triangulation at the result level, rather than simply saying that certain 

&nbsp;<!----------------------------------------------------------------------->  

#### Standardisation across study designs

Standardising across different measures of ex

Want best information across lipids, and so standardised across different measures

Fixing directions of effect - get everything pointing the same way

&nbsp;<!----------------------------------------------------------------------->  

### Alternative approaches

#### E-values

Present as an alternative to putting priors on the level of bias due to confounding.

E-values work the other way around - get result then work out how strong a biasing factor would have to be to negate the result. IN other words, they represent an estimate ho how strong the total residual confounding would have to be in order to full explain away the observed result.[@vanderweele2017]

One major problem is that they can only be used to evaluate negating biases, not other biases. 

How strong unmeasured confounding would have to be in order to explain the observed effect.

Heavily criticised in a range of papers.

Also, no useful to focus on a specific bias in the context of risk of bias domains

As an example, I calculated the E-value required to attenuate the hamrful association observed between statin use and vascular dementia in the CPRD analysis ( `r hold()`` ) presented in Chapter \@ref(cprd-heading). Assuming an outcome prevalence of <15%, an E-value of 3.31 was identified

This calculation was performed using the XXX R package.

<!-- TODO Ensure that the example is provided first, as you then go on to disparage it - in the example given, the main driver of bias is likely to be confounding (though some may be due to misclassification) -->

However, this approach is only useful if the only source of bias in a result is due to uncontrolled confounding (as assessed by a domain-based risk of bias tool).

Otherwise, it's interpretation is more challenging, as the biasing effect is incorrectly assinged complete to confoudning, thus overestimating the expected effect of confounding. 

the contribution of confounding to the bias in a result, and while it may be applicable if the only bias assessed to


&nbsp;<!----------------------------------------------------------------------->  

&nbsp;<!----------------------------------------------------------------------->  

### Need for new method

As the need and appetite for snthesis of different, future iterations of the risk of bias tools should take this into account. Simple things like harmonising the risk of bias levels across tools would be a good first move towards a more integrate suite of tools. Similarly, software that implements the risk-of-bias tools should both allow for direction of bias question and carefully consider how this data will be exported.


Can I suggest any empirical studies that need to be performed? Average strength of immortal time bias/etc?

While the limitations inherent to this method are important, and limit the , they reflect a more detailed appreciation of the complexities of risk of bias assessment and triangulation as whole (i.e. not applying expected directions of effects to a ). 

This approach also builds on existing approaches employed previously by "exploding out" the results of a systematic review/meta-analysis and considering the effects of bias in each individual result seperately. This more granular approach is to be preferred over assigning a bias judgement and direction to the summary effect produced by a meta-analysis,  which may mask the different biases applicable to each unique result.


&nbsp;<!----------------------------------------------------------------------->  

## Conclusion

Triangulation is a promising developing field, somewhat hamstrung by the limited understanding of the impact of biases at the meta-epidemiological level.

This chapter has demonstrated a repurposed framework for quantitative triangulation, exploiting existing methods in evidence synthesis and developments in the assessment of different risks of bias. 

It also introduce a new way to visualise the biases at work in a particular result, rather than making assumptions about the type and directions of bias at the study design level as suggested by previous work on this topic. 

Finally, it highlighted the limitations of current methods for triangulation in the absence of informative priors for the impact of biases across the 


\newpage

## References



