---
bibliography: bibliography/references.bib
csl: bibliography/nature.csl
output:
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::word_document2: 
      toc: false
      toc_depth: 3
      reference_docx: templates/word-styles-reference-01.docx
      number_sections: false 
  bookdown::html_document2: default
documentclass: book
---

```{r, echo = FALSE, warning=FALSE, message=FALSE}
source("R/helper.R")
knitr::read_chunk("R/05-Code-CPRD-Analysis.R")
doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
```


<!----------------------------------------------------------------------------->
(ref:covariateDef-caption) Definition of covariates adjusted for in the full-adjusted model. The codelists used to define the majority of these covariates were originally created for use in a previously published analysis.[@walker2020] while others were built on or adapted from previous published work.[@khan2010; @taylor2016; @wright2017]

(ref:covariateDef-scaption) Covariates adjusted for.

(ref:covariateDef-cell1) Charlson index implemented using Read code lists.[@khan2010] Code lists based on those by Taylor et al.[@taylor2016]

(ref:covariateDef-cell2) Most recent of recorded value (current, former or never) or Read code indicating a recorded value. Code lists based on those by Wright et al.[@wright2017]

```{r covariateDef-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->
